An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-11 EconGrowth2.Rnw
Changed size of historical graph to be significantly narrower.

<<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalPlot()
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
spghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
spghettiPlot(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
spghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

>>>>

<<Historical_Lattice_Graph, fig.pos="H", fig.width=3, fig.height=7.0, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalPlot()
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
spaghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
spaghettiPlot(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
spaghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}
